Forward Modeling Galaxy Size in a Cosmological Context

### 2017-10-04 paper/galsize_paper.tex
Starting to sketch intro

@@

\ben
\item \citet{vanderwel_etal14,kawamata_etal15,shibuya_etal15,huertas_company_etal13a,huang_etal17} - high redshift studies of size evolution with HST
\item \citet{shankar_etal17,yoon_kim17,huang_leauthaud_etal17} - high mass
\item \citet{huang_etal13} - multiple component profiles
\een

>>>>

%%%%%%%%  cosmology  %%%%%%%%
\newcommand{\lcdm}{\Lambda{\rm CDM}}

@@

In the $\lcdm$ framework of cosmological structure formation, galaxies form at the centers of dark matter halos. Highly complex and nonlinear baryonic processes regulate galaxy formation, and the quest for a fine-grained understanding of these processes is one of the chief goals of theoretical astrophysics today.

Observationally, many properties of observed galaxies exhibit remarkably tight scaling relations. Among the most fundamental of these relations is the strong correlation between galaxy size and stellar mass and luminosity. The scaling of galaxy size with galaxy mass is well-measured in the local Universe \citep{shen_etal03,guo_etal09,huang_etal13,zhang_yang17} and at high-redshift \citep{trujillo_etal04,vanderwel_etal14,kawamata_etal15,shibuya_etal15,huertas_company_etal13a,lange_etal15,huang_etal17}.

These well-measured scaling relations are challenging to faithfully recover using ab initio galaxy formation methods such as hydrodynamical simulations and semi-analytic models, and provide useful boundary conditions for the calibration of such modeling efforts \citep{khochfar_silk06,dutton_etal10,hopkins_etal10a,bottrell_etal17b}. The precision cosmology program also depends critically on accurate modeling of galaxies, so that cosmological parameter inference can be confidently conducted without undue interference from uncertainty in baryonic physics \citep{LSST_science,LSST_galaxies}.
